Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-02-10 paper/paper.tex
added a few figures to paper Tested everything on node23.

\begin{figure}
  \includegraphics[width=3cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
  \includegraphics[width=3cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
  \caption{Box plots of Mannik shapes for sizes at the lower stability
    threshhold.  Both shapes have longer axis of roughly 2.2$\mu m$.}
  \label{box-mannik}
\end{figure}
Decreasing the cell size in succesive steps, we can see as well the
critical size at which the cell oscillations are quickly damped out.
Figure~\ref{box-mannik} shows box plots of the largest cells simulated
whose oscilltions relax into the steady state solution.  Both have a
long axis of roughly 2.2$\mu m$, in agreement with theory.

\fixme{I'm also waiting for data to come in that will hopefully show
  cells so small that no oscillations take place.  We can put this in
  as well}

@@

>>>>

\begin{figure}
  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
  \caption{Box plots of Mannik shapes for sizes at the lower stability
    threshhold.  The vertical axis shows stacked and changing over
    time the total number of proteins that are of four different
    compound stages and in the different sections of the cell.  Both
    shapes have longer axis of roughly 2.2$\mu m$.}
  \label{box-mannik}
\end{figure}
Decreasing the cell size in succesive steps, we can see as well the
critical size at which the cell oscillations are quickly damped out.
Figure~\ref{box-mannik} shows box plots of the largest cells simulated
whose oscilltions relax into the steady state solution.  Both have a
long axis of roughly 2.2$\mu m$, in agreement with theory.

@@

\begin{figure}
  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
  \caption{Box plots of triangle shapes for sizes at the lower stability
    threshhold.  The vertical axis shows stacked and changing over
    time the total number of proteins that are of four different
    compound stages and in the different sections of the cell.}
  \label{box-triangle}
\end{figure}
